LAGOS lake depth

### 2020-11-24 tables/02_model_metrics.Rmd
add mape to table 1

dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds") %>%
  mutate_if(is.numeric, function(x) as.character(round(x, 2))) %>%
  mutate(rsq = as.numeric(rsq)) %>%
  mutate(rsq = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_real_,
    TRUE ~ rsq)) %>%
  mutate(rmse = round(as.numeric(rmse), 1)) %>%
  mutate(rmse = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_character_,
    TRUE ~ paste0(rmse, " m"))) %>%
  mutate(model = gsub("maxdepth_", "", model)) %>%
  mutate(model = gsub("false", "proxy", model)) %>%
  tidyr::separate(model, c("slope", "distance")) %>%
  dplyr::select(slope, distance, everything(), -.estimator)

>>>>

dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds") %>%
  mutate_if(is.numeric, function(x) as.character(round(x, 2))) %>%
  mutate(rsq = as.numeric(rsq)) %>%
  mutate(rsq = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_real_,
    TRUE ~ rsq)) %>%
  mutate(rmse = round(as.numeric(rmse), 1)) %>%
  mutate(rmse = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_character_,
    TRUE ~ paste0(rmse, " m"))) %>%
  mutate(mape = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_character_,
    TRUE ~ paste0(mape, " %"))) %>%
  mutate(model = gsub("maxdepth_", "", model)) %>%
  mutate(model = gsub("false", "proxy", model)) %>%
  tidyr::separate(model, c("slope", "distance")) %>%
  dplyr::select(slope, distance, everything(), -.estimator)
